Comprehensive study of the global phase diagram of the $J$-$K$-$\Gamma$ model on a triangular lattice

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 14:01

In order to better understand the quantum phases identified by the ED method, we also perform classical Monte Carlo simulations. We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$. For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24 \times 24$ triangle lattice with periodic boundary conditions. A whole Monte Carlo step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ Monte Carlo steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{align}
    \vec{S}_{i} = \frac{\vec{h}_{i}^{loc}}{|\vec{h}_{i}^{loc}|} S,
\end{align}
with
\begin{align}
    \vec{h}_{i}^{loc} = \sum_{\langle j \rangle} J \vec{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
\end{align}
\added[swang]{
    and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
    \begin{eqnarray}
        \vec{S}_i^{new} & = &\frac{2 (\vec{S}_i^{old} \cdot \vec{h}_i^{loc}) \vec{h}_i^{loc}}{|\vec{h}_i^{loc}|^2}-\vec{S}_i^{old}.
    \end{eqnarray}
}
For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.

@@

In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e., $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively. Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i). Thus, this further confirms that the stripe-A phase extents to a large region in the phase diagram. In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ for one of the new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.
\added[swang]{The difference between stripe-A, stripe-B and stripe-C lies in that they have different moment directions, which we will discuss in detail later.}

@@

\added[swang]{The most commonly used physcial quantity to distinguish different quantum phases is the order parameter. The order parameter of FM, stripe, 120$^\circ$ N\'eel and dual N\'eel states can be defined as $\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector of these magnetically ordered states. However since the cluster ground state does not spontaneously break the symmetry and corresponds to a superposition of all possible degenerate orderings, the calculated ground state average may give no useful information.}

>>>>

In order to better understand the quantum phases identified by the ED method, we also perform classical Monte Carlo simulations. We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$. For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24 \times 24$ triangle lattice with periodic boundary conditions. A whole Monte Carlo step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ Monte Carlo steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{align}
    \vec{S}_{i} = \frac{\vec{h}_{i}^{loc}}{|\vec{h}_{i}^{loc}|} S,
\end{align}
with
\begin{align}
    \vec{h}_{i}^{loc} = \sum_{\langle j \rangle} J \vec{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
\end{align}
\added[swang]{and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
\begin{eqnarray}
    \vec{S}_i^{new} & = &\frac{2 (\vec{S}_i^{old} \cdot \vec{h}_i^{loc}) \vec{h}_i^{loc}}{|\vec{h}_i^{loc}|^2}-\vec{S}_i^{old}.
\end{eqnarray}
}For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.

@@

In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e., $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively. Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i). Thus, this further confirms that the stripe-A phase extents to a large region in the phase diagram. In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ for one of the new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.

\added[swang]{Although the singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ show that there are phase transitions between stripe-A, stripe-B and stripe-C (see Appendix \ref{apx:PhaseBoundary} for details), the differences between these phases cannot be seen from the SSFs, which show the same characteristic wave vector [Fig.~\ref{fig:StructureFactors}(a), (b), (c) and (d)]. In fact, the most commonly used physcial quantity to distinguish different quantum phases is the order parameter. For the magnetically ordered phases, such as the stripe phases discussed here, the order parameter can be defined as $\bm{m}(\bm{Q})=\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector. Thus, both the ordering vector and the moment direction are the defining characteristic. The difference between the stripe-A, stripe-B and stripe-C phases lies in that they have different moment directions, which we will discuss in detail later in the paper.}

@@
